{\large\bf Publications \bf}
% \scriptsize($^{(\ast)}$: Co-primary author)}
\medskip\hrule height 0.1pt
%{}
\vspace{1mm}


\begin{longtable}{p{1mm}p{14.5cm}}

\hspace{-24 mm} [MobiSys'26] 	&\textbf{Min-Yue Chen}, Yiwen Hu, Yu-An Chen, Chi-Yu Li, Tian Xie, Guan-Hua Tu, ''Insecurity of Lost/Stolen Phone Reporting Services: Vulnerabilities, Attacks, and Countermeasures,'' \textit{conditionally accepted} by \emph{ACM International Conference on Mobile Systems, Applications, and Services} (\textbf{ACM MobiSys}), June 21-25, 2026, Cambridge, UK.
[\textbf{Acceptance Rate: 68/302 = 22.51\%}]\\

\\

\hspace{-24 mm} [GetMobile'25] 	&	
Jingwen Shi, Sihan Wang, \textbf{Min-Yue Chen}, Guan-Hua Tu, Tian Xie, Man-Hsin Chen, Yiwen Hu, Chi-Yu Li, and Chunyi Peng,
``IMS is Not That Secure on Your 5G/4G Phones,''
\emph{ACM GetMobile Magazine: Mobile Computing and Communications} (\textbf{GetMobile}), Volume: 29, Issue: 1, pp. 20-24, April, 2025.
\textcolor{Blue}{\textbf{Invited Article \& Research Highlights}} \\

\\


\hspace{-23 mm} [MobiCom'24] 	&	
Yiwen Hu, \textbf{Min-Yue Chen}, Haitian Yan, Chuan-Yi Cheng, Guan-Hua Tu, Chi-Yu Li, Tian Xie, Chunyi Peng, Li Xiao, and Jiliang Tang,
``Uncovering Problematic Designs Hindering Ubiquitous Cellular Emergency Services Access,''
accepted by \emph{ACM International Conference On Mobile Computing And Networking} (\textbf{ACM MobiCom}), September 30 - October 4, 2024, Washington, D.C., United States.
[\textbf{Acceptance Rate: 103/494 = 20.85\%}] \\

\\

\hspace{-23 mm} [MobiCom'24] 	&	
Jingwen Shi, Sihan Wang, \textbf{Min-Yue Chen}, Guan-Hua Tu, Tian Xie, Man-Hsin Chen, Yiwen Hu, Chi-Yu Li, and Chunyi Peng,
``IMS is Not That Secure on Your 5G/4G Phones,''
accepted by \emph{ACM International Conference On Mobile Computing And Networking} (\textbf{ACM MobiCom}), September 30 - October 4, 2024, Washington, D.C., United States.
[\textbf{Acceptance Rate: 103/494 = 20.85\%}]\\

\\


\hspace{-14 mm} [ToN'24] 		& 	
\textbf{Min-Yue Chen}, Yiwen Hu, Guan-Hua Tu, Chi-Yu Li, Sihan Wang, Jingwen Shi, Tian Xie, Li Xiao, Chunyi Peng, Zhaowei Tan, and Songwu Lu,
``Taming the Insecurity of Cellular Emergency Services (9-1-1): From Vulnerabilities to Secure Designs,''
\emph{IEEE/ACM Transactions on Networking} (\textbf{ToN}), Volume 32, Issue: 4, pp. 3076-3091, Aug. 2024.
[\textbf{Impact Factor: 3.79}]  \\

\\

\hspace{-14 mm} [ToN'24] 		& 	
Sihan Wang, Tian Xie, \textbf{Min-Yue Chen}, Guan-Hua Tu, Chi-Yu Li, Xinyu Lei, Po-Yi Chou, Fucheng Hsieh, Yiwen Hu, Li Xiao, Chunyi Peng,
``Dissecting Operational Cellular IoT Service Security: Attacks and Defenses,''
\emph{IEEE/ACM Transactions on Networking} (\textbf{ToN}), Volume: 32, Issue: 2, pp. 1229-1244, April 2024.
[\textbf{Impact Factor: 3.79}]  \\

\\




\hspace{-24 mm} [GetMobile'23] 	& Yiwen Hu$^{(\ast)}$, \textbf{Min-Yue Chen$^{(\ast)}$}, Guan-Hua Tu, Chi-Yu Li, Sihan Wang, Jingwen Shi, Tian Xie, Li Xiao, Chunyi Peng, Zhaowei Tan, and Songwu Lu,
``Unveiling the Insecurity of Operational Cellular Emergency Services (911): Vulnerabilities, Attacks, and Countermeasures,''
\emph{ACM GetMobile Magazine: Mobile Computing and Communications} (\textbf{GetMobile}), Volume: 27, Issue: 1, pp. 39-43, March, 2023.
\textcolor{Blue}{\textbf{Invited Article \& Research Highlights}} \newline\textbf{($\ast$): Co-primary author, denotes equal contribution}\\

\\

\hspace{-23 mm} [MobiCom'22] 	&	
Yiwen Hu$^{(\ast)}$, \textbf{Min-Yue Chen$^{(\ast)}$}, Guan-Hua Tu, Chi-Yu Li, Sihan Wang, Jingwen Shi, Tian Xie, Li Xiao, Chunyi Peng, Zhaowei Tan, and Songwu Lu,
``Uncovering Insecure Designs of Cellular Emergency Services (911),''
\emph{ACM International Conference On Mobile Computing And Networking} (\textbf{ACM MobiCom}), October 17–21, 2022, Sydney, Australia, pp 703–715.
[\textbf{Acceptance Rate: 57/315 = 18.1\%}]
\textcolor{Blue}{[\textbf{Media Coverage: \href{https://msutoday.msu.edu/news/2023/making-emergency-calls-more-secure}{MSU Today}, \href{https://www.wilx.com/2023/04/25/msu-researchers-discover-vulnerability-911-calls-made-cell-phones/}{Wilx TV}, \href{https://www.woodtv.com/video/msu-researchers-get-1-2m-to-improve-911-call-security/8598883/}{Wood TV}, \href{https://player.fm/series/the-wils-morning-wake-up/guan-hua-tu-jillian-tang}{WILS Morning Wake-Up}, \href{https://www.homelandsecuritynewswire.com/dr20230427-making-emergency-calls-more-secure}{Homeland Security News}, \href{https://www.isssource.com/boosting-security-for-cellular-emergency-calls/}{ISSSource}, \href{https://www.eurekalert.org/news-releases/987600}{EurekAlert}}]}
\textbf{\href{https://www.cse.msu.edu/~ghtu/911-award.png}{\color{Red}{Best Community Paper Award - Runner Up}}, \textbf{\href{https://www.sigmobile.org/grav/publications/research-highlights}{\color{Red}{ACM SIGMOBILE Research Highlights}}}, {\color{Red}{AT\&T Security Award}}} \newline\textbf{($\ast$): Co-primary author, denotes equal contribution}\\

\\



\end{longtable}


% {\large\bf Under Submission/Under Review}
% \medskip\hrule height 0.1pt
% %{}
% \vspace{1mm}


% \begin{longtable}{p{1mm}p{14.5cm}}
%     \hspace{-24 mm} [MobiSys'26] 	&\textbf{Min-Yue Chen}, Yiwen Hu, Yu-An Chen, Chi-Yu Li, Tian Xie, Guan-Hua Tu, ``Insecurity of Lost/Stolen Phone Reporting Services: Vulnerabilities, Attacks, and Countermeasures''

% \end{longtable}
